The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Moved comparison table to chapter 5, removed landscape page
Indents.
Modified chapter 6 and 7 to be more structurally coherent

@@

	The largest repository of decentralization attempts is located at http://redecentralize.org. The struggle and pains of these projects illustrates the difficulty of decentralization. No projects succeeded in creating an alternative internet infrastructure. This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.

@@

	Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}. One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet. This ranges from self hosted cloud applications, to crypto currencies, to anonymous networks.

	We made a significant contribution to this project index.
	As a contribution to (anonymous) decentralized system research, we have improved and updated the list of these decentralized systems. For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh. This table is available on the same Github repository.

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we found that this most accurately represented projects that have been established for some time and have been active in the past days. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.

@@

	So although clear differences aren't directly noticeable, we hope that his will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.

@@

	We explained how the leading privacy-enhancing technology Tor works and which components define a Tor network. Furthermore, we looked at the main disadvantages and problems Tor is currently facing. We investigated the issues around decentralization. After that, we've written which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.

@@

	For the first time we document in detail, the amount of wasted effort and pain spent in decentralization. The current generation of technology lead by Tor still has room for improvement, while the next generation is only just appearing on the horizon.

\begin{landscape}
	% Zelfde volgorde als hoofdstukken
	% Deze bij hoofdstuk 5 plaatsen!!!
	% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
	\begin{table}[p]
		\centering
		\include{tbl-currentsystems}
		\caption{A comparison of decentralized peer-to-peer overlay networks.}
		\label{tbl:comparison}
	\end{table}
\end{landscape}

>>>>

		% Zelfde volgorde als hoofdstukken
		% Enkel de rijen met stukjes in tekst (I2P? Salsa?)
		\begin{table}[t]
			\centering
			\include{tbl-currentsystems}
			\caption{A comparison of decentralized peer-to-peer overlay networks.}
			\label{tbl:comparison}
		\end{table}

@@

	The largest repository of decentralization attempts is located at http://redecentralize.org. The aim of this repository is to \textquoteleft get decentralized products into the hands of billions\textquoteright \cite{aboutredecentralizeorg}. One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet. The struggle and pains of these projects illustrates the difficulty of decentralization. No projects succeeded in creating an alternative internet infrastructure. The projects range from self hosted cloud applications, to crypto currencies, to anonymous networks.

@@

	%Redecentralize.org is a project that describes itself with the aim to \textquoteleft start of a new information revolutions\textquoteright~by \textquoteleft bringing decentralized in the hands of billions\textquoteright~\cite{aboutredecentralizeorg}. One of the ways they do this, is by maintaining a Github repository\footnote{Found at https://github.com/redecentralize/alternative-internet} with projects that in some way help to decentralize the internet.

	We made a significant contribution to this project index. We have improved and updated the list of these decentralized systems. For each of the listed systems, we have created an entry in a table that shows statistics such as the total lines of code (LOC), age, number of contributors and commits, activity and (main) programming language, sourced from Ohloh. This table is available on the same Github repository.

	An excerpt of the table is included as table \ref{tbl:altinternet}. In this instance, we chose to sort the table on the number of commits, because we find that this most accurately represents both the maturity and activity of the projects. Other statistics such as LOC might not be very relevant on their own, because some projects include big libraries or other projects.

@@

	So although clear differences aren't directly noticeable, we hope that this comparison will provide more insight into which systems are more serious and mature than others, while also showing which one are still actively maintained.

@@

	We explained how the leading privacy-enhancing technology Tor works and which components define a Tor network. Furthermore, we looked at the main disadvantages and problems Tor is currently facing. We investigated the issues around decentralization and compared systems that currently have a decentralized structure and/or mechanism.

@@

	For the first time we document in detail, the amount of wasted effort and pain spent in decentralization. The current generation of technology lead by Tor still has room for improvement, while the next generation is only just appearing on the horizon. The major problems involving decentralization are excruciatingly difficult to overcome. None of the projects have succeeded in making the internet secure and private.
